---
title: "EDA"
author: "Meghan Duarte"
date: "2026-05-23"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Clean the Data

```{r, message=FALSE, warning=FALSE}
library(dplyr)
library(tidyverse)
library(ggplot2)
library(tsibble)
library(feasts)
library(fable)
```

```{r}
singapore <- read.csv('BirthsAndFertilityRatesAnnual.csv')
```

```{r}
clean_1 <- singapore |>
  filter(DataSeries %in% c("Total Fertility Rate (TFR)", "Total Live-Births")) 
```

```{r}
clean_2 <- pivot_longer(clean_1,
                        cols = starts_with("X"),
                        names_to = "Year",
                        values_to = "Value",
                        values_transform = list(Value = as.character))
```

```{r}
clean_3 <- mutate(clean_2, Year = str_remove(Year, "X"))

clean_4 <- clean_3 |> mutate(Year = as.numeric(Year), Value = as.numeric(Value))

clean_data <- clean_4 |>
  pivot_wider(names_from = DataSeries, values_from = Value)
singapore <- clean_data |>
  as_tsibble(index = Year)
singapore
```

```{r}
singapore |> autoplot(`Total Fertility Rate (TFR)`) +
  labs(title = "Total Fertility Rate (1960-2024)",
       caption = "Fig. 1 Plot of the Total Fertility Rate in Singapore from 1960 to 2024.",
       y = "Total Fertility Rate",
       x = "Year") +
  theme(plot.caption = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5))
```

```{r}
singapore |> autoplot(`Total Live-Births`) +
  labs(title = "Total Live-Births (1960-2024)",
       caption = stringr::str_wrap("Fig. 2 Plot of the Total Live-Births in Singapore from 1960 to 2024 shows that it follows a roughly similar trend as the plot of the Total Fertility Rate."), width = 80,
       y = "Total Live-Births",
       x = "Year") +
  theme(plot.caption = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5))
```

While figure 1 and figure 2 look different we can see that they show spikes and drops at similar points. There is a spike around 1988 in the plot of Total Fertility Rate and a large spike around the same year in the plot of the Total Live-Births. This can also be seen with a spike around 1972, as well as drops around 1969, 1987, 2003, and 2024.   


```{r}
singapore |> autoplot(log(`Total Fertility Rate (TFR)`)) +
  labs(title = "Log-Transformed Total Fertility Rate (1960-2024)",
       caption = stringr::str_wrap("Fig. 3 Plot of the Total Fertility Rate with a log transformation in Singapore from 1960 to 2024."), width = 80,
       y = "log(Total Fertility Rate)",
       x = "Year") +
  theme(plot.caption = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5))
```


```{r}
singapore |> autoplot(log(`Total Live-Births`)) +
  labs(title = "Log-Transformed Total Live-Births (1960-2024)",
       caption = stringr::str_wrap("Fig. 4 Plot of the Total Live-Births with a log transformation in Singapore from 1960 to 2024."), width = 80,
       y = "log(Total Live-Births)",
       x = "Year") +
  theme(plot.caption = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5))
```

```{r}
singapore |> features(log(`Total Fertility Rate (TFR)`), unitroot_kpss)
```
Table 1. KPSS test of the log transformed Total Fertility rate in Singapore from 1960-1924. The p-value is 0.01, which is significant at the $\alpha = 0.05$ significance level. 

```{r}
singapore |> features(log(`Total Live-Births`), unitroot_kpss)
```

Table 2. KPSS test of the log transformed Total Live-Birth rate in Singapore from 1960-1924. The p-value is 0.01, which is significant at the $\alpha = 0.05$ significance level. 

Figures 3 and 4, along with the p-values from tables 1 and 2 both being significant at the 0.05 significance level, show that a log transformation seems to help a bit but they both still need to be stabilized more. To do this, they will be differenced. 

```{r}
singapore |> autoplot(difference(log(`Total Fertility Rate (TFR)`), 1)) +
  labs(title = "First-Order difference of Log TFR (1960-2024)",
       caption = stringr::str_wrap("Fig. 5 Plot of the first-order difference of the log transformed Total Fertility Rate in Singapore from 1960 to 2024."), width = 80,
       y = "Change in log(TFR)",
       x = "Year") +
  theme(plot.caption = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5))
```


```{r}
singapore |> autoplot(difference(log(`Total Live-Births`), 1)) +
  labs(title = "First-Order difference of Log TLB (1960-2024)",
       caption = stringr::str_wrap("Fig. 6 Plot of the first-order difference of the log transformed Total Live-Births in Singapore from 1960 to 2024."), width = 80,
       y = "Change of log(TLB)",
       x = "Year") +
  theme(plot.caption = element_text(hjust = 0.5),
        plot.title = element_text(hjust = 0.5))
```

Plots 5 and 6 no longer show a downward trend with a first-order difference of the log transform of each variable.

```{r}
TFR <- difference(log(singapore$`Total Fertility Rate (TFR)`), 1)
                  
TLB <- difference(log(singapore$`Total Live-Births`), 1)
```


```{r}
singapore |> features(TFR, unitroot_kpss)
```
Table 3. KPSS test of the first-order differenced log transformed Total Fertility rate in Singapore from 1960-1924. The p-value is 0.09, which is not significant at the $\alpha = 0.05$ significance level.

```{r}
singapore |> features(TLB, unitroot_kpss)
```

Table 4. KPSS test of the first-order differenced log transformed Total Live-Birth rate in Singapore from 1960-1924. The p-value is 0.1, which is not significant at the $\alpha = 0.05$ significance level. 


Tables 3 and 4 confirm what figures 5 and 6 showed, when both Total Live-Births and Total Fertility rate are log transformed and then differenced, they are stationary. In a KPSS test, if the p-value is less than 0.05, the null-hypothesis that the series is stationary, is rejected. However, if the p-value is greater than 0.05, the null-hypothesis is accepted and the series is found to be stationary. 

















